---
title: "Exploring Tmap"
output: html_document
date: "2024-12-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exploration of Tmap library for Geographical Visualisation

Created a map of the world using the function `tm_shape()`. Layers can be added with `+` operator, in this case `tm_polygons()` is used.

```{r}
library(tmap)
data("World")

tmap_mode("plot")

tm_shape(World) + 
  tm_polygons("HPI")
```

Each map can be plotted as a static image or viewed interactively using `plot` or `view` modes respectively. Mode can be set with function `tmap_mode()` and toggling between the modes can be done with `switch ttm()` which stands for toggle thematic map. 

```{r}
tmap_mode("view")

tm_shape(World) + 
  tm_polygons(c("HPI", "economy")) + 
  tm_facets(sync=TRUE, ncol=2)
```

```{r}
tmap_mode("plot")

data("NLD_muni")
NLD_muni$perc_men = NLD_muni$pop_men / NLD_muni$population * 100 

tm_shape(NLD_muni) + 
  tm_polygons("perc_men", palette="RdYlBu") + 
  tm_facets(by="province")
```

```{r}
library(tmap)
library(sf)

shpfile_path = "~/Sync/data_science_daily/data/LTARoadCameraSHP/LTA_Road_Enforcement_Camera.shp"
enforcement_camera = st_read(shpfile_path)

tmap_mode("view")
tm_shape(enforcement_camera) + 
  tm_symbols(size=0.01, col="red") + 
  tm_basemap("OpenStreetMap")
```

```{r}
eld_boundary = st_read("~/Sync/data_science_daily/data/ElectoralBoundaryDataset.kml")

tmap_mode("view")
tmap_options(check.and.fix = TRUE)

tm_shape(eld_boundary) + 
  tm_fill(col="Name", alpha=0.3, palette = "Set3", legend.show=FALSE) +
  tm_borders() +
  tm_shape(enforcement_camera) + 
  tm_symbols(size=0.01, col='red') +
  tm_basemap("OpenStreetMap")
```



